A Bayesian networks approach to infer social changes in burials in northeastern Taiwan during the European colonization period

### 2021-04-24 analysis/paper/paper.Rmd
fixed the typo of ERGM

<!-- Bayesian inference for Exponential Random Graph Models --> 
Bayesian approaches to ERGMs are effective tools for network modeling by incorporating prior information about the network configurations (details in Supplementary Online Materials) to better understand dependencies of network variables and overcome computational issues of ERGMs [@Caimo2017; @Lehmann2020]. Prior information is derived from previous data or assumptions derived from the context of our data. An important advantage that Bayesian modeling has over traditional ERGMs is the application of Markov chain Monte Carlo (MCMC) simulation using the approximate exchange algorithm [@Caimo2011]. With the exchange algorithm, Bayesian ERGMs avoid doubly-intractable computations by directly sampling from the not normalized part of the posterior, which alleviates the computational problems and gives better convergence results. This enables us to deal with complicated dependence patterns with ease, providing better estimations for complex social network models with heterogeneous data [@Caimo2017; @Snijders2006]. By fitting an ERMG with the approximate exchange algorithm, a Bayesian approach generates posterior probabilities that incorporate our sample data and prior information to estimate the effect of each ERGM parameter in our models [@Caimo2015; @Nemmers2019]. This allows robust and interpretable uncertainty quantification by examining the posterior mean and 95% credible intervals [@Caimo2017bayesian]. In addition, Bayesian approaches are useful to deal with missing data, which is often a problem leading to misinterpretation of networks, especially for archaeological studies. @Koskinen2010 shows that the effect of missing data can be reduced with Bayesian modeling that can accurately predict, on average, 80% of the ties when a third of data is missing.

>>>>

<!-- Bayesian inference for Exponential Random Graph Models --> 
Bayesian approaches to ERGMs are effective tools for network modeling by incorporating prior information about the network configurations (details in Supplementary Online Materials) to better understand dependencies of network variables and overcome computational issues of ERGMs [@Caimo2017; @Lehmann2020]. Prior information is derived from previous data or assumptions derived from the context of our data. An important advantage that Bayesian modeling has over traditional ERGMs is the application of Markov chain Monte Carlo (MCMC) simulation using the approximate exchange algorithm [@Caimo2011]. With the exchange algorithm, Bayesian ERGMs avoid doubly-intractable computations by directly sampling from the not normalized part of the posterior, which alleviates the computational problems and gives better convergence results. This enables us to deal with complicated dependence patterns with ease, providing better estimations for complex social network models with heterogeneous data [@Caimo2017; @Snijders2006]. By fitting an ERGM with the approximate exchange algorithm, a Bayesian approach generates posterior probabilities that incorporate our sample data and prior information to estimate the effect of each ERGM parameter in our models [@Caimo2015; @Nemmers2019]. This allows robust and interpretable uncertainty quantification by examining the posterior mean and 95% credible intervals [@Caimo2017bayesian]. In addition, Bayesian approaches are useful to deal with missing data, which is often a problem leading to misinterpretation of networks, especially for archaeological studies. @Koskinen2010 shows that the effect of missing data can be reduced with Bayesian modeling that can accurately predict, on average, 80% of the ties when a third of data is missing.
